%!TEX TS-program = xelatex
\documentclass[10pt,twoside]{friggeri-cv}

\usepackage{fontawesome,url}

\begin{document}
\header{arjang}{talattof}
       {principal data scientist}


% In the aside, each new line forces a line break
\begin{aside}
  \section{contact}
    \href{mailto:arjang@umich.edu}{\scriptsize  \texttt{arjang@umich.edu \faEnvelope}}
    \href{https://www.linkedin.com/in/arjang-talattof-a974845a/}{\scriptsize  \texttt{linkedin \faicon{linkedin}}}
    \href{http://arjology.github.io}{\scriptsize  \texttt{github \faicon{github}}}
    \href{http://www.flickr.com/photos/talattof}{\scriptsize  \texttt{flickr \faicon{globe}}}
    \scriptsize  \texttt{+44 7555117012 \faPhone}
    \scriptsize  \texttt{+01 6467700275 \faPhone}
  \section{languages}
    \scriptsize trilingual english/french/persian
    \scriptsize conversational spanish \& italian
  \section{technologies}
    \item Apache Kafka, Spark, Zookeeper
    \item Cassandra/NoSQL, DataStax Enterprise, Graph Database, Neo4J, Redis
    \item Gremlin, Java, Mathematica, Matlab, Perl, Python (pandas, scipy, numpy, scikit-learn), R, Scala, Tinkerpop
    \item Unix/Linux (Centos, Debian, FreeBSD, Gentoo, RedHat), Shell scripting (bash, sed, awk)
    \item Machine Learning (Gaussian Processes, SVM, Neural Networks, Decision Trees, Random Forests)
  \section{activities}
    soccer {\scriptsize \faicon{trophy}}
    photography {\scriptsize \faicon{camera-retro}}
\end{aside}

\section{about}

Data scientist and big data engineer in London. Python, Java \& Scala developer. Spark and graph database
enthusiast. Applied mathematician by training. Scholar of gastrointestinal motility variation. UK Tier 1 Exceptional Talent Visa \& US citizenship.

\section{technical summary}

\begin{entrylist}
  \entry
    {\scriptsize \faicon{cloud-upload}}
    {Massively scaled graph database analytics.}
    {production}
    {\scriptsize Leveraging Cassandra and Spark (Spark Streaming) for large-scale graph networks and analyses including:\\
    Building tools to explore and analyze graph data in a distributed cloud-based cluster.
    Developing machine learning algorithms and automation of real-time entity resolution / disambiguation at scale.
    Dealing with 10\textsuperscript{7} (eventually reaching 10\textsuperscript{9}) transactions daily utilizing Kafka and Spark Streaming to ingest massive amounts of data through an ETL pipeline.
    successfully deploying working beta software to client; revenue increase from \$1.8M to \$6.0M; internal investment by firm (\$0.5M) to generalize new capability based on client deliverable.}
  \entry
    {\scriptsize \faicon{stethoscope}}
    {Stochastic fluid transit model}
    {research}
    {\scriptsize  Developed in Java to to study the effects of physiological variations on drug transit, dissolution, and absorption\\
    Pulsatile, non-deterministic approach; 
    Application of a non-homogeneous Poisson process; 
    Based on sampling from and imaging of small bowel free water content}
  \entry
    {\scriptsize \faicon{search}}
    {Study of large data sets}
    {research}
    {\scriptsize Goal to identify patterns in drug product submissions and failures in the Office of Generic Drugs}
  \entry
    {\scriptsize \faicon{bar-chart}}
    {Analysis of noisy gastrointestinal pressure signals}
    {research}
    {\scriptsize Wavelet-based peak detection and kernel density estimation;
    Machine learning, Gaussian process regression \& PCA for signal classification;
    Completed in Python with SciPy/NumPy/SciKit packages}
  \entry
    {\scriptsize \faicon{code}}
    {Java interface for handling parameters and their values with syntax highlighting}
    {production}
    {\scriptsize Managing dynamic parameters that control processing pipeline;
    Parameters and database fields (JDBC Data\_Port for MySQL);
    Pipeline source queue management and error handling}
\end{entrylist}

\section{professional experience}

\begin{entrylist}
  \entry
    {\scriptsize aug 17 - pres}
    {Scape Technologies}
    {principal data sciencist}
    {\scriptsize \emph{Building core date flow and analysis pipeline for location-based recognition, allowing devices to see and remember their surroundings \& augment the world around them. Cloud side infrastructure allows ordinary mobile devices to enhance the world around them by overlaying digital items onto the physical world, both indoors and outdoors, using machine vision \& artificial intelligence.}}
  \entry
    {\scriptsize aug 16 - jul 17}
    {Deloitte Consulting LLP}
    {senior data science consultant}
    {\scriptsize \emph{Mission Analytics in Business Model \& Transformation/Strategy \& Operations. Supporting senior government executives in the development of the organization's strategy and business process; assisting in development, collection, analysis, and reporting of data by leverage big data and machine learning technologies; serving as domain knowledgeable resource in advising the Deloitte team and client on tools and techniques to improve workflow.}}
  \entry
    {\scriptsize jul 15 - aug 16}
    {U.S. Food and Drug Administration}
    {research fellow}
    {\scriptsize \emph{Division of Quantitative Methods and Modeling in the Office of Research and Standards within the Office of Generic Drugs. 
Applying mathematical analysis to physiological/molecular based models for drug absorption, bioavailability, distribution and effectiveness. Using large data sets to improve the prediction and regulatory decision making for generic drugs.}}
  \entry
    {\scriptsize mar 06 - aug 07}
    {Department of Lunar \& Planetary Sciences\\University of Arizona}
    {java developer}
    {\scriptsize \emph{Developing open-source software for data analysis for the HiRISE instrument on the Mars Reconnaissance Orbiter. Co-funded by NASA and JPL.}}
\end{entrylist}

\pagebreak
    
\section{education}

\begin{entrylist}
  \entry
    {\scriptsize 2015}
    {Ph.D. {\normalfont Pharmaceutical Sciences}}
    {University of Michigan}
    {\scriptsize Dissertation: \emph{Mechanistic Analysis and Quantification of Gastrointestinal Motility: Physiological Variability and Plasma Level Implications.}}
  \entry
    {\scriptsize 2011}
    {M.Sc. {\normalfont Pharmaceutical Sciences}}
    {University of Michigan}
    {}
  \entry
    {\scriptsize 2009}
    {M.Sc. {\normalfont Computational Biology}}
    {New York University}
    {}
  \entry
    {\scriptsize 2006}
    {B.Sc. {\normalfont Mathematics}}
    {University of Arizona}
    {}
  \end{entrylist}
  
\section{publications}

\begin{small}

Hens, B, Y Tsume, M Bermejo, P Paixao, M Koenigsknecht, J Baker, W Hasler, R Lionberger, J Fan, J Dickens, K Shedden, B Wen, J Wysocki, R Lobenberg, A Lee, A Fioritto, G E Amidon, A Yu, G Benninghoff, N Salehi, \emph{A Talattof}, D Sun, G L Amidon. Low Buffer Capacity Along The Human Gastrointestinal Tract: Implications for in vivo Dissolution and Absorption of Ionizable Drugs. \emph{Molecular Pharmaceutics}, Submitted for publication May 2017.

La Count, T D,  Q Zhang, J Hao, \emph{A Talattof}, P Ghosh, S G Raney, G B Kasting, S K Li. Modeling temperature-dependent skin absorption and dermal clearance for transdermal and topical drug applications. \emph{AAPS Journal}. Submitted for publication April 2017.

\emph{Entity Knowledge Graph: Real-Time Massively Scaled Graph Analytics to Disambiguate Data}, March 2017.
Poster presentation at Deloitte US Data Science Summit, Dallas, TX.

Ni, Z, \emph{A Talattof}, J Fan, E Tsakalozou, S Sharan D Sun H Wen X Zhang L Zhao. Physiologically Based Pharmacokinetic and Absorption Modeling for Osmotic Pump Products. \emph{AAPS Journal}. 2017, 1-9.

Hens, B, M Corsetti, R Spiller, L Marciani, T Vanuytselc, J Tackc, \emph{A Talattof},  G L Amidon, M Koziolek, W Weitschies, C G Wilson, R J Bennink, J Brouwers, P Augustijns. Exploring gastrointestinal variables affecting drug and formulation behavior: Methodologies, challenges and opportunities. \emph{International Journal of Pharmaceutics}. 2016, 519(1-2):79-97.

Chow, E.C.Y., \emph{Talattof, A.}, Tsakalozou, E. et al. Using Physiologically Based Pharmacokinetic (PBPK) Modeling to Evaluate the Impact of Pharmaceutical Excipients on Oral Drug Absorption: Sensitivity Analyses. \emph{AAPS Journal}, 2016.

Talattof, A. \emph{et al}. Gastrointestinal Motility Variation and Implications for Plasma Level Variation: Oral Drug Products. \emph{Mol. Pharmaceutics}, 2016, 13 (2), 557-567

\emph{Fasted State Motility-Dependent Transit and Dissolution of Ibuprofen}, October 2015.
Poster presentation at AAPS 2015 Conference, Orlando, FL.

Min, K. A. \emph{et al}. Massive Bioaccumulation and Self-Assembly of Phenazine Compounds in Live Cells. \emph{Adv Sci.} 2015 Jun;2(8)

\emph{Fasted-State Motility-Dependent Gastric Emptying and Plasma Level Variation: Bioequivalence Implications}, November 2014.
Poster presentation at AAPS 2014 Conference, San Diego, CA.

Min, K. A. \emph{et al}. The Extracellular Microenvironment Explains Variations in Passive Drug Transport across Different Airway Epithelial Cell Types. \emph{Pharm Res.} 2013 Aug;30(8):2118-32. 

\emph{Quantitative Analysis of Transmission Electron Microscopy Image Data Reveals a Supramolecular Organization Mediating Clofazimine Sequestration in Macrophages}, November 2013.
Poster presentation at AAPS 2013 Conference, San Antonio, TX.

\emph{Morphometric analysis of multilamellar drug-membrane aggregates from electron microscopy images}, June 2012. 
Poster presentation at CYTO2012 Conference, Leipzig, Germany.

\end{small}


\end{document}
